Declarative Integration of Interactive 3D Graphics into the World-Wide Web:\\Principles, Current Approaches, and Research Agenda

### 2013-04-26 Web3D2013-Dec3D/paper.tex
some words added...

Similarly, \textit{generic data containers}~(7) should be based on TypedArrays \cite{TypArr12} with appropriate interfaces for efficient modification of the data. These containers should be general enough to support meshes, animations, shaders, etc. This concept is very close to our efforts regarding \textit{external data containers}~(8) and their efficient transmission~\cite{Behr12,Trevett12}. Given that the generic data containers are close to buffer objects in recent graphics APIs, we aim \textit{3D geometry definitions}~(9) close to OpenGL primitives.

@@

Essential DOM elements are a basic set of pre-defined \textit{shaders}~(11), which should be enough for most use cases. Advantages are that they do not entail timing attack issues and that they can adapt to any target device. However, the design should not obstruct programmable shaders in the future. HTML elements such as \verb|<img>|, \verb|<video>|, and \verb|<canvas>| can be used as \textit{textures}~(12), whereas elements such as \verb|<svg>| and \verb|<html>| can serve as interactive textures.

>>>>

Similarly, \textit{generic data containers}~(7) should be based on TypedArrays \cite{TypArr12} with appropriate interfaces for efficient modification of the data. These containers should be general enough to support meshes, animations, shaders, etc. This concept is very close to our efforts regarding \textit{external data containers}~(8) and their efficient transmission~\cite{Behr12,Trevett12}. Given that the generic data containers are close to vertex buffer objects in recent graphics APIs, we aim \textit{3D geometry definitions}~(9) close to OpenGL primitives.

@@

Essential DOM elements are a basic set of pre-defined \textit{shaders}~(11), which should be enough for most use cases. Advantages are that they do not entail timing attack issues and that they can adapt to any target device. However, the design should not obstruct programmable shaders in the future. HTML elements such as \verb|<img>|, \verb|<video>|, and \verb|<canvas>| can be used as \textit{textures}~(12), whereas elements such as \verb|<svg>| and \verb|<html>| could serve as interactive textures -- once the corresponding security issues are resolved.
